Sound Automated Synthesis of Digital Controllers

### 2016-10-11 paper/paper.tex
Minor changes

The Lemma~\ref{lemma:eq_int_stab} provides the necessary conditions for synthesis of digital controllers able to stabilize closed loop system, considering plant parametric uncertainties ($\Delta G_{P}(z)$), quantisation noises ($\nu_{1}$ and $\nu_{2}$) and FWL effects in digital controllers. Based on it, the model for plant uncertainty due quantisation noise ($\Delta G(z)$ may be disregarded if the conditions on Lemma~\ref{lemma:eq_int_stab} are attended and if the quantisation noise is bounded.

The quantisation noise is indeed bounded, since assumption~\ref{whitenoise} and the Lemmas~\ref{lemma:variance} and~\ref{lemma:boundednoise} are true.

>>>>

The Lemma~\ref{lemma:eq_int_stab} provides the necessary conditions for synthesis of digital controllers able to stabilize closed loop system, considering plant parametric uncertainties ({\it i.e.}, $\Delta G_{P}(z)$), quantisation noises ($\nu_{1}$ and $\nu_{2}$) and FWL effects in digital controllers. Based on it, the model for plant uncertainty due quantisation noise ({\it i.e.}, $\Delta G_{Q}(z)$) may be disregarded if the conditions on Lemma~\ref{lemma:eq_int_stab} are attended and if the quantisation noise is bounded.

The quantisation noise is indeed bounded, since the following assumption~\ref{whitenoise} and the Lemmas~\ref{lemma:variance} and~\ref{lemma:boundednoise} are true.
